Variational Monte Carlo on bosonic systems

### 2018-04-03 project_1/article/article.tex
Review drift force stub

    \subsection{The drift force}
        A disadvantage in the use of the brute force Metropolis-Hastings
        algorithm is that we might be spending much computational resources in
        an uninteresting part of configuration space. To make smarter moves we
        will use the Metropolis-Hastings algorithm with the additions of
        \emph{Importance Sampling}  (which will be discussed in due time). This
        alteration of the algorithm is dependent on the \emph{drift force} of
        the system.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \sum_{k = 1}^N
            \vf{F}_k(\vf{r})
            =
            \sum_{k = 1}^N
            \frac{2\nabla_k\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
            \label{eq:drift_force}
        \end{align}
        Using this expression we are able to move towards parts of
        configuration space where the gradient increases or decreases yielding a
        better choice of movements. We will mainly be interested in the drift
        force of a single particle $k$.

>>>>

    \subsection{The drift force}
        A disadvantage in the use of the brute force Metropolis-Hastings
        algorithm is that we might be spending much computational resources in
        an uninteresting part of configuration space. To make smarter moves we
        will use the Metropolis-Hastings algorithm with the additions of
        \emph{Importance Sampling}  (which will be discussed in due time). This
        alteration of the algorithm is dependent on the \emph{drift force} of
        the system\footnote{Also known as the \emph{quantum force}}.
        \begin{align}
            \vf{F}(\vf{r})
            &=
            \sum_{k = 1}^N
            \vf{F}_k(\vf{r})
            =
            \sum_{k = 1}^N
            \frac{2\nabla_k\Psi_T(\vf{r})}{\Psi_T(\vf{r})}.
            \label{eq:drift_force}
        \end{align}
        Using this expression we are able to move towards parts of
        configuration space where the gradient increases or decreases yielding a
        better choice of movements. We will mainly be interested in the drift
        force of a single particle $k$ as the Monte Carlo sampling involves
        choosing a single particle at a time.
